A Comparison of the Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-06-27 mt-marathon.2012/PBML_article.tex
from google doc

\title{Title of My Article\titlelinebreak{} with a Forced Linebreak}

@@

\begin{equation}
%  score = Sum_i _member_T(weight_i * score_i) + Sum_i _member_L(weight_i * score_i) + weight_wp * word-penalty
\end{equation}

where T is the set of translation models, and L is the set of sequence models.

>>>>

\title{A Comparison of the Synchronous-CFG \titlelinebreak{} Decoder Implementations}

@@

\begin{equation}
  score = \sum_{i \in T}(weight_i * score_i) + \sum_{i  \in L} (weight_i * score_i) + weight_{wp} * word-penalty
\end{equation}

where $T$ is the set of translation models, and $L$ is the set of sequence models.
